Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
update numbers
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52662 72bbbca6-d526-0410-a7d9-f06f51895060
baseline
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52664 72bbbca6-d526-0410-a7d9-f06f51895060

For our current task, each of the texts have been limited to two languages i.e. the primary and the secondary language. Hence the type of chunking tags are limited to these. The evaluation statics shown in the Table mention two values for each of the experiment conducted on the three bilingual language datasets. The first, is the percentage of correctly detected phrases, which is the overall precision and the second is the number of phrases in the data that were found by the chunker, which is the overall recall.

@@

\begin{table}
\begin{center}
\begin{tabular}{|lc|rr|rr|rr|}
\hline
            & & \multicolumn{2}{c}{Irish---English} & \multicolumn{2}{c}{Welsh---English} & \multicolumn{2}{c}{Breton---French}  \\
\hline
                                        &         &  Irish &       English & Welsh & English & Breton & French \\
\multirow{2}{*}{\texttt{baseline}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{langid2}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{langid3}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{wordlist}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{bigram}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{wordlist+bigram}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}
\end{center}

@@

>>>>

For our current task, each of the texts have been limited to two languages i.e. the primary and the secondary language. Hence the type of chunking tags are limited to these. The evaluation statics shown in the Table mention two values for each of the experiment conducted on the three bilingual language datasets. The first, is the percentage of correctly detected phrases, which is the overall precision and the second is the number of phrases in the data that were found by the chunker, which is the overall recall. \\

The different techniques used for the sub-segmenting task are described as follows -

1. Baseline - This is the most naive method of classification, we used the language identification tool langid.py \cite{lui2012langid} on the whole dataset and labelled all the individual lines according to this single major classification. \\

@@

\begin{table}
\begin{center}
\begin{tabular}{|lc|rr|rr|rr|}
\hline
            & & \multicolumn{2}{c}{Irish---English} & \multicolumn{2}{c}{Welsh---English} & \multicolumn{2}{c}{Breton---French}  \\
\hline
                                        &         &  Irish &       English & Welsh & English & Breton & French \\
\multirow{2}{*}{\texttt{baseline}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{langid2}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{langid3}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{wordlist}} &  $p$ &  32.50 & 28.57        & 26.69 & 40.91 & 57.41 & 33.96 \\
                                       & $r$  & 23.64   & 26.09       & 26.03 & 33.75 & 47.69 & 33.33 \\
\hline
\multirow{2}{*}{\texttt{bigram}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\multirow{2}{*}{\texttt{wordlist+bigram}} &  $p$ &  2.5 & 0.0        & 0.0 & 0.0 & 0.0 & 0.0 \\
                                       & $r$  & 2.5   & 0.0       & 0.0 & 0.0 & 0.0 & 0.0 \\
\hline
\end{tabular}
\end{center}

@@

(CHECKLATER-FORMATTING)
1. Baseline - Negligible precision and recall show that the task of detecting sub-segments in complex and there needs to be more improvement in the methodology.
